Fusion Moves for Correlation Clustering

### 2014-11-07 paper/egpaper_for_review.tex
mychanges

\section{Energy Based Hierarchical Clustering (EBHC)}

Agglomerative hierarchical clustering (HC) is widely used
in graph / energy segmentation
\cite{arbelaez_2006}.
Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.

HC can be used to find approximate
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

>>>>

\section{Energy Based Hierarchical Clustering (EHC)}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.
Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update.

We propose to use EHC find
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.
